---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
options(datatable.prettyprint.char = 30L)
```

# treasury

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![R-CMD-check](https://github.com/m-muecke/treasury/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/m-muecke/treasury/actions/workflows/R-CMD-check.yaml)
[![CRAN status](https://www.r-pkg.org/badges/version/treasury)](https://CRAN.R-project.org/package=treasury)
<!-- badges: end -->

## Overview

The goal of treasury is to provide a simple and modern interface to the [US treasury XML feed](https://home.treasury.gov/treasury-daily-interest-rate-xml-feed) for daily interest rates.

## Installation

You can install the released version of **treasury** from [CRAN](https://CRAN.R-project.org) with:

```{r, eval = FALSE}
install.packages("treasury")
```

And the development version from [GitHub](https://github.com/) with:

```{r, eval = FALSE}
# install.packages("pak")
pak::pak("m-muecke/treasury")
```

## Usage

treasury functions are prefixed with `tr_` and follow the naming convention of the XML feed.

```{r usage, message = FALSE, dpi = 300}
library(treasury)

yield_curve <- tr_yield_curve(2023)
head(yield_curve)
```

```{r plot, message = FALSE, echo = FALSE, dpi = 300}
library(ggplot2)

yield_curve[maturity == "10 year"] |>
  ggplot(aes(x = date, y = rate)) +
  geom_line() +
  theme_minimal() +
  theme(
    legend.title = element_blank(),
    legend.position = "top",
    plot.title = element_text(face = "bold"),
    plot.caption = element_text(
      hjust = 0, vjust = 0, size = 8, margin = margin(10, 0, 0, 0)
    ),
    panel.grid.major.y = element_line(color = "black", linewidth = 0.2),
    panel.grid.major.x = element_blank(),
    panel.grid.minor = element_blank(),
    axis.text = element_text(color = "black"),
    axis.title = element_blank(),
    plot.margin = margin(10, 10, 10, 10)
  ) +
  labs(title = "US Treasury Yield Curve 2023 (10 Year Maturity)")
```

## Related work

- [ustyc](https://github.com/mrbcuda/ustyc) - R package to download and parse the US Treasury yield curve data
- [ustfd](https://github.com/groditi/ustfd) - R client for US Treasury Fiscal Data API
