---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# treasury

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![R-CMD-check](https://github.com/m-muecke/treasury/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/m-muecke/treasury/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

## Overview
The goal of treasury is to provide a simple and modern interface to the [US treasury XML feed](https://home.treasury.gov/treasury-daily-interest-rate-xml-feed) for daily interest rates.
The main difference to other packages is that it's a modern implementation using the [httr2](https://httr2.r-lib.org) package.

## Installation

You can install the development version of treasury from [GitHub](https://github.com/) with:

```{r, eval = FALSE}
# install.packages("pak")
pak::pak("m-muecke/treasury")
```

## Usage

treasury functions are prefixed with `tr_` and follow the naming convention of the XML feed.

```{r demo, message = FALSE, dpi = 300}
library(treasury)

yield_curve <- tr_yield_curve(2020)
yield_curve

library(ggplot2)

subset(yield_curve, maturity == "10 year") |>
  ggplot(aes(x = date, y = rate)) +
  geom_line()
```

## Related work

- [ustyc](https://github.com/mrbcuda/ustyc) - R package to download and parse the US Treasury yield curve data
